---
title: "Lab 03 - Nobel laureates"
author: "Eric, Ryan, Eddie, Shirley, Chen" 
date: "`r Sys.Date()`"
output: html_document
---


### Load packages and data

```{r load-packages, message = FALSE, warning=FALSE}
library(tidyverse) 
```

```{r reading-nobel-data., message = FALSE}
nobel <- read_csv("data/nobel.csv")
```

### Exercise 1

#### Narrative


There are `r nrow(nobel)` rows and `r ncol(nobel)` columns, hence there are `r nrow(nobel)` observations and `r ncol(nobel)` variables. Each row represents a Nobel laureate.


### Exercise 2



```{r nobel-living}
nobel_alive <- nobel %>%
  filter(is.na(country) == FALSE , gender !="org", is.na(died_date) == TRUE)


```



#### Narrative

There are `r nrow(nobel_alive)` rows hence there are `r nrow(nobel_alive)` observations


### Exercise 3

#### Code

```{r facet-bar-plot}
nobel_living <- nobel_alive %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )

nobel_living_science <- nobel_living %>% 
  filter(
    category %in% c("Physics", "Medicine", "Chemistry", "Economics")
    )

ggplot(data = nobel_living_science) + 
  geom_bar(
    mapping = aes(y = country_us)) +
  facet_wrap(~ category) + 
  labs(x = "Number of living Nobel laureates",
       y = "Country",
       title = "Living Nobel laureates and the countries they were based in")
```

#### Narrative

The visualisation supports Buzzfeed's narrative that most living Nobel laureates were in the US when they won their prize, as the bar for the US is longer in every STEM category than the bar for laureates outside the US, suggesting many more of the laureates were based in the US. This disparity is greatest in Economics and smallest in Chemistry.


### Exercise 4

#### Code

```{r born-country-us}
# remove this comment and add your code here
```


### Exercise 5

#### Narrative

*Remove this text and add your answer here.*

#### Code

```{r facet-bar-plot-redo}
# remove this comment and add your code here
```


### Exercise 6

#### Code

```{r born-country}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*